Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
comment out weather_fips code

```{r}
#Find the top 15 FIPS by number of reporting stations during Ike-2008 (Warning: Takes a long time)
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} 
#Ike FIPS without data: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
ike_top <- ike_table$fips
#Find the top 15 FIPS by number of reporting stations for Alex-2010:
my_fips <- alex_fips[c(1:2, 4:6, 8, 10, 12:14, 16:18)]
my_stations <- NA
alex_table <- expand.grid(my_fips, my_stations)
colnames(alex_table) <- c("fips", "station")
for(fips in my_fips){
        alex_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        alex_table[alex_table$fips == fips, "station"] <- max(alex_weather$daily_weather$prcp_reporting)    
} 
#Alex FIPS without data: 3, 7, 9, 11, 15, 19   
alex_table <- alex_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
alex_top <- alex_table$fips
fips_table <- rbind(alex_table, ike_table)
fips_table <- fips_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
all_fips <- fips_table$fips
all_fips <- unique(all_fips)
```

@@

```{r}
ike_weather <- county_timeseries(fips = ike_top[1:2], 
                                 percent_coverage = 0, 
                                 date_min = "2008-09-01", 
                                 date_max = "2010-09-14", var = "PRCP", 
                                 out_directory = "~/tmp/ike_ex")

>>>>

```{r}
#Find the top 15 FIPS by number of reporting stations during Ike-2008 (Warning: Takes a long time)
#my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
#my_stations <- NA
#ike_table <- expand.grid(my_fips, my_stations)
#colnames(ike_table) <- c("fips", "station")
#for(fips in my_fips){
        #ike_weather <- weather_fips(fips = fips,
                                    #date_min = "2008-09-01",
                                    #date_max = "2008-09-14",
                                    #var = "PRCP")
        #ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
#} 
#Ike FIPS without data: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
#ike_table <- ike_table %>%
        #arrange(desc(station)) %>%
        #slice(1:15)
#ike_top <- ike_table$fips
#Find the top 15 FIPS by number of reporting stations for Alex-2010:
#my_fips <- alex_fips[c(1:2, 4:6, 8, 10, 12:14, 16:18)]
#my_stations <- NA
#alex_table <- expand.grid(my_fips, my_stations)
#colnames(alex_table) <- c("fips", "station")
#for(fips in my_fips){
#        alex_weather <- weather_fips(fips = fips,
#                                    date_min = "2008-09-01",
#                                    date_max = "2008-09-14",
#                                    var = "PRCP")
#        alex_table[alex_table$fips == fips, "station"] <- max(alex_weather$daily_weather$prcp_reporting)    
#} 
#Alex FIPS without data: 3, 7, 9, 11, 15, 19   
#alex_table <- alex_table %>%
#        arrange(desc(station)) %>%
#        slice(1:15)
#alex_top <- alex_table$fips
#fips_table <- rbind(alex_table, ike_table)
#fips_table <- fips_table %>%
#        arrange(desc(station)) %>%
#        slice(1:15)
#all_fips <- fips_table$fips
#all_fips <- unique(all_fips)
```

@@

```{r}
county_timeseries(fips = ike_top[1:2], 
                  percent_coverage = 0, 
                  date_min = "2008-09-01", 
                  date_max = "2010-09-14", var = "PRCP", 
                  out_directory = "~/tmp/ike_ex")
